### 2023-08-22 resilience-safe-up.tex
up

Let us remark that coverability reduce
to resilience when  $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$,
as $s \to^* \uparrow t$ 
reduces to $\Safe$-resilience for $\Safe = \uparrow t$ and $\Bad = \downarrow s$.
%
Let us recall that the coverability problem for strongly increasing well-structured nets is undecidable~\cite{FMP-ic04}, hence the strongly increasing well-structured nets are not completion-post-effective hypothesis nor have the pred-basis hypothesis.
%
Moreover, this implies from the reduction that resilience for strongly increasing well-structured nets is  undecidable. Hence resilience for WSTS in general is undecidable.

@@

>>>>

@@

Let us remark that coverability reduce
to resilience when  $\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$,
as $s \to^* \uparrow t$ 
reduces to $\Safe$-resilience for $\Safe = \uparrow t$ and $\Bad = \downarrow s$.
\mathieu{No longer the case here since $\Bad$ needs be the complement of $\Safe$.}
Let us recall that the coverability problem for strongly increasing well-structured nets is undecidable~\cite{FMP-ic04}, hence the strongly increasing well-structured nets are not completion-post-effective hypothesis nor have the pred-basis hypothesis.
%
Moreover, this implies from the reduction that resilience for strongly increasing well-structured nets is  undecidable. Hence resilience for WSTS in general is undecidable.
